Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density

### 2018-05-29 manuscript.tex
Section 3 reviewed

Because of the spurious variations in RV's caused by active regions, a crucial step of the entire analysis is to correct the initially estimated RV's in order to retrieve a set of RV's containing ideally only the possibly pure Doppler-shift coming from the exoplanets. In order to reach this goal, we propose to consider a linear combination of the RV's having as covariates the amplitude parameter A, the BIS SPAN (or $\gamma$), the FWHM (or SN FWHM) and the interaction between the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM and the interaction between $\gamma$ and SN FWHM in the SN case). We propose the following function to correct the RV's from stellar activity:
%
\begin{equation}
RV_{\text{stellar activity}}= \beta_{0} + \beta_{1} A + \beta_{2} \gamma + \beta_{3} \text{SN FWHM} + \beta_{4} (\gamma  \text{SN FWHM})+\epsilon,
\label{eq:RV:correction}
\end{equation}
%
where $\beta_{0}$ is the intercept and $\epsilon$ is the vector of the errors with mean equal to $0$ and covariance matrix equal to $\sigma^{2}I$ ($I$ defined as the identity matrix).

While the parameters BIS SPAN and FWHM have already been introduced and used in several analysis \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}, we propose in addition to include the contrast parameter $A$ and a variable that quantifies the interaction between BIS SPAN (or $\gamma$) and FWHM (or SN FWHM). The inclusion of the contrast parameter $A$ is justified by the fact that the presence for instance of a spot produces also changes in the amplitude of the CCF and not only on its asymmetry or width \citep[see e.g. Fig. 2 in ][]{Dumusque-2014b}.
%%
%\begin{figure*}[htbp]
%   \centering
%\includegraphics[height = 2.5in]{FTS_solar_CCFs_whyWeAddAlsoPARAM_A.pdf} 
%   \caption{The presence of a spot on the photosphere of a star produces changes on the amplitude of the CCF (also known as contrast) and not only on its asymmetry or width. This very same plot has been originally presented by \citep{Dumusque-2014b} when introducing the Spot Oscillation And Planet (SOAP) 2.0 simulator.}
%    \label{fig:spotA}
%\end{figure*}
%%

The reasons for including in Eq.~\ref{eq:RV:correction} a variable that quantifies the interaction between BIS SPAN (or $\gamma$) and FWHM (or SN FWHM) will be better justified through the results of the examples presented in Sec.\ref{sec:soap}. We point out however that while the association between in this case BIS SPAN  (or $\gamma$) and FWHM (or SN FWHM) means that the values of one variable relate to the values of the other (since in this case we have two quantitative variables we talk about correlation), with the term interaction we mean that the effect that one variable has on the RV's is not constant. In particular the effect differs at different values of the other values. %As a consequence of this, if two variables are interacting the may or may not be associated.

In order to show the goodness of this correction, a statistical test on the parameters $\beta_{0}$, $\beta_{1}$, $\beta_{2}$, $\beta_{3}$ and $\beta_{4}$ is presented, where the null hypothesis is $H_{0}: \beta_{i}=0$, for $i=0,\dots,4$. The level for not rejecting the null hypothesis is fixed equal to $0.05$. The coefficient of multiple correlation $R^2$ is introduced in order to explain how well this linear combination addresses the variability of the RV variation induced by stellar activity.

As final remark we recall that, when working with a linear regression, there are several ways to select the variables to include in the model. While usually the stepwise technique takes place \citep{efroymson1960multiple,hocking1976biometrics}, the proposed function defined in Eq.~\ref{eq:RV:correction} that corrects from stellar activity is the result of statistical and astronomical considerations. In particular we checked that the correlations between the proposed parameters were not approaching one: if it were the case, the matrix needed to calculate the estimates would have been singular, hence non invertible. This problem is known in statistic with the term multicollinearity. A detailed discussion of the topic can be found in the book by \citep{belsley1991}. In the literature there are examples of stars presenting a high correlation between the contrast parameter $A$ and the FWHM \citep{Dumusque:2017aa,Feng:2017aa}. In the analyses of the presented work, we did not find any correlation between the contrast parameter $A$ and the FWHM (or between the contrast parameter $A$ and the SN FWHM) exceeding $0.66$ for all the analyzed stars and therefore the problem of multicollinearity is avoided. For the interpretation of the coefficients, we centered on the mean all the variables considered in the linear regression defined in Eq.~\ref{eq:RV:correction}. Last, when proposing interactions between covariates, we found that only the one between the width and the asymmetry of the CCF is statistically helpful to explain spurious variations in RV's caused by stellar activity. Consequently, in the present work, the interaction between other variables are not used as covariates.

>>>>

\xavier{When fitting for planetary signals in RV data, it is common to include in the fitted model, linear dependencies with the BIS SPAN and the FWHM, to take into account the signal induced by stellar activity \citep[e.g.][]{Dumusque:2017aa,Feng:2017aa}.
%Some people also include the \logrhk, however, \citet{Feng-2018} show that this is probably not a good choice as \logrhk and RV are not well correlated.
In this paper, we propose to add additional parameters in the model to correct for stellar activity: first the amplitude parameter A of the CCF, generally referred to as the CCF contrast, and the interaction between the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM in the SN case). The stellar activity correction we propose can therefore be written as:}
%
\begin{equation}
RV_{\text{stellar activity}}= \beta_{0} + \beta_{1} A + \beta_{2} \gamma + \beta_{3} \text{SN FWHM} + \beta_{4} (\gamma  \text{SN FWHM})+\epsilon,
\label{eq:RV:correction}
\end{equation}
%
where $\beta_{0}$ is the intercept and $\epsilon$ is the vector of the errors with mean equal to $0$ and covariance matrix equal to $\sigma^{2}I$ ($I$ defined as the identity matrix). 
The inclusion of the contrast parameter $A$ is justified by the fact that the presence of a spot on the stellar surface produces a changes in the amplitude of the CCF and not only on its asymmetry or width \citep[see e.g. Fig. 2 in ][]{Dumusque-2014b}.
The reasons for including in Eq.~\ref{eq:RV:correction} a variable that quantifies the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM) will be better justified through the results of the examples presented in Sec.\ref{sec:soap}. 
\xavier{This interaction term allows to take into account cases when for different values of SN FWHM (or FWHM), the linear coefficient $\beta_{2}$ for $\gamma$ (or BIS SPAN) varies}. \xavier{Umberto, Jessi, is this correct ?}
%while the association between in this case BIS SPAN and FWHM (or $\gamma$ and SN FWHM) means that the values of one variable relate to the values of the other (since in this case we have two quantitative variables we talk about correlation), with the term interaction we mean that the effect that one variable has on the RV's is not constant. In particular the effect differs at different values of the other values. %As a consequence of this, if two variables are interacting the may or may not be associated.

In order to show the goodness of this correction, a statistical test on the parameters $\beta_{0}$, $\beta_{1}$, $\beta_{2}$, $\beta_{3}$ and $\beta_{4}$ is presented, where the null hypothesis is $H_{0}: \beta_{i}=0$, for $i=0,\dots,4$. The level for not rejecting the null hypothesis is fixed to $0.05$. The coefficient of multiple correlation $R^2$ is introduced in order to explain how well this linear combination addresses the variability of the RV variation induced by stellar activity.

When working with a linear regression, there are several ways to select the variables to include in the model. While usually the stepwise technique is used \citep{efroymson1960multiple,hocking1976biometrics}, the proposed function defined in Eq.~\ref{eq:RV:correction}, that accounts for stellar activity, is the result of statistical and astronomical considerations. In particular we checked that the correlations between the proposed parameters were not approaching one: if it was the case, the matrix needed to calculate the estimates would be singular, hence non invertible. This problem is known in statistics with the term multicollinearity. A detailed discussion of the topic can be found in the book by \citet{belsley1991}. \xavier{It is common to see some correlation between the amplitude parameter $A$ and the FWHM (or SN FWHM) of the CCF. However, in the analysis of real data presented in this work, we never observed a correlation coefficient exceeding $0.66$ and therefore, the problem of multicollinearity is avoided. Finally, we investigate as well the statistical significant of the interaction term between $A$ and the width, and $A$ and the asymmetry of the CC, however, those interaction were relevant for accounting for stellar signal.}
